Graph-based Neuron Agglomeration using 3D Skeletons

### 2017-11-08 papers/cvpr2018/3_evaluation.tex
paper: added in Toufiq edits

\subsubsection{Segmentation Pipeline and Baseline}
\label{sec:neuroproof}
Our algorithm takes the output of a supervoxel based agglomeration strategy such as NeuroProof or GALA. For our experiments we use the output from NeuroProof (CITE). We generate voxel affinities from the raw image data using the U-Net architecture \cite{ronneberger2015u}. The Zwatershed algorithm (CITE) creates an oversegmentation of the neurons given these voxel affinities. We input the raw image data, the voxel affinities, and the oversegmentation into NeuroProof which performs a hierarchical agglomeration strategy to merge the supervoxels into larger and larger segments. Two neighboring segments receive a merge-likelihood score based on various extracted features such as the distribution of affinities along the segment boundary. A random forest classifier generates probabilities based on these features. (TODO: TOUFIQ ADD HERE)

>>>>

\subsubsection{Segmentation Pipeline and Baseline}
\label{sec:neuroproof}
The segmentation on [Cite Kasthuri Cell2015] dataset was computed by agglomerating 3D supervoxels produced by zwatershed [Cite Zlatesky arXiv2015] from 3D affinity predictions. 
A recent study by Funke et.al. [Funke arXiv2017] demonstrated superior performance of such method over existing ones on anisotropic data. 
We learned 3d affinities in x,y,z using MALIS [Cite Turaga, NIPS 2009] loss with a U-net [Ronneberger, MICCAI 2015]. 
We apply the zwatershed algorithm, with suitable parameters, to compute an 3D over-segmentation of the volume. 
The resulting 3D over-segmentation is then agglomerated using the technique of [Parag, Plos One 2015] to generate the final segmentation. The VI values at different stopping thresholds of agglomeration correspond to the points on the curve plotted in Figure YYY.

We have collected two 1000x1000x1000 voxel (10x10x10 um) volumes from the authors of [Takemura, elife 2017]. 
Based on the authors' suggestion, we applied the algorithm of [Parag, ICCV 2015] that showed improved performance on this dataset than the pipeline used in [Takemura, elife2017]. 
The segmentation framework of [Parag, ICCV 2015] learns voxel and supervoxel classifier with an emphasis to minimize under-segmentation error and, at the same time, is capable of producing lower over-segmentation that standard algorithms. 
This algorithm first computes a multi-channel 3D predictions for membrane, cell interior, mitochondria, etc. 
The membrane prediction channel is utilized to produce an over-segmented volume by 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly same parameters for the publicly available code for this algorithm and used different agglomerations thresholds to plot the VI error curve.
